---
title: "java-oop-game-gradle-sprintboot-mongodb-r-quarto"
author: "hedskul"
date: "`r Sys.Date()`"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  
  fig.path = "figs/"
)
```
### Java - Principles of Object-Oriented Design

## Installation guide

```bash
# git 
git clone https://github.com/hedskul/java-oop-game-gradle-sprintboot-mongodb-r-quarto.git
cd java-oop-game-gradle-sprintboot-mongodb-r-quarto
```

<!-- # python -m venv -h -->
<!-- # -m mod : run library module as a script (terminates option list) -->
<!-- # virtual environment -->
<!-- python -3.12 -m venv .venv -->

<!-- # win -->
<!-- # bash -->
<!-- .venv/Scripts/activate -->
<!-- # unix -->
<!-- source .venv/bin/activate -->

<!-- # pygame==2.6.1 -->
<!-- pip install -r requirements.txt -->
<!-- python src/hello-world-pygame.py -->

## Installation guide

<!-- PyCharm - Settings -> Project: Python Interpreter -->
<!-- -> Virtualenv -> Base Python: 3.12.x  -->

<!-- PyCharm - Added IDE and project folder to Windows Exclusion list -->

<!-- PyCharm - ModuleNotFoundError: No module named 'pygame' -->
<!-- pip install pygame -->
<!-- https://www.pygame.org/wiki/GettingStarted -->

<!-- Terminal -->
<!-- ``` CLI -->
<!-- python -m pip install --upgrade pip -->
<!-- pip install pygame -->
<!-- pip freeze > requirements.txt -->
<!-- ``` -->

## README is created using rmarkdown, knitr, and renv

This is an R Markdown format used for publishing markdown documents to GitHub.
When you click the **Knit** button all R code chunks are run
and a markdown file (.md) suitable for publishing to GitHub is generated.

1: Install R
<https://cran.rstudio.com/>

2: Install RStudio - RStudio requires R 3.6.0+.
<https://posit.co/download/rstudio-desktop/>

3 Recreate RStudio environment.
RStudio: File -> Open Project
Browse to python-oop-pygame-r-reticulate-quarto.Rproj

4 R Console:

``` r
install.packages("renv")
renv::restore()
```

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
